\section{Introduction}
\label{sec:intro}
This is for Introduction. You can add any sections you want.

\subsection{Language}

All manuscripts must be in either English or Korean.

\subsection{Paper length}

The final report must not exceed eight pages, excluding references. There is no penalty for using fewer than eight pages. Quality is valued more than quantity.

\subsection{Required contents}

Your report must include the following sections, \textbf{including but not limited to}:

\begin{itemize}
    \item \textbf{Summary and Novelty:} Clearly summarize the main idea of the paper and explicitly explain what is novel compared to prior work.
    
    \item \textbf{Survey of Related Work:} Review key related works and explain how they are connected to, or differentiated from, the target paper.
    
    \item \textbf{Detailed Explanation of the Method (in Your Own Words):} Provide a thorough explanation of the proposed method using your own interpretation and language, not by copying the original text.
    
    \item \textbf{Limitations and Potential Failure Cases:} Discuss weaknesses, limitations, and scenarios where the method may fail or perform poorly.
    
    \item \textbf{Your Own Improvement Ideas:} Propose your own ideas for improving the method or extending it to new problems.
    
    \item \textbf{Answers to Additional Questions from Peers:} After the presentation, additional questions will be given. Your written answers to these questions must be included in the final report.
    
    \item \textbf{Each Teammate's Contribution:} Clearly describe the individual contributions of each team member.
\end{itemize}

\subsection{How to add citations}
\begin{enumerate}
  \item Go to Google Scholar (https://scholar.google.com/).
  \item Search the paper that you want to include.
  \item Click ``Cite'' button under the summarization of the paper.
  \item Click ``BibTex'' button at left-below.
  \item Ctrl+C, V to \texttt{main.bib} file.
  \item Include the citation: e.g., ResNet~\cite{he2016deep}.
\end{enumerate}


\subsection{Final notes}
For this report, the order of authors is considered meaningless. Please list all authors in alphabetical order.
Good luck!
